### 2021-09-14 paper/localpsf.tex
Working through Tuckers comments

%We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
%\begin{equation}
%	\label{eq:wi_optimization_problem_intro}
%	\begin{aligned}
%		\min_{w_i \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
%		\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
%	\end{aligned}
%\end{equation}
%Here $\Delta$ is the Laplacian on $\Omega$, $H^2_N(\Omega)$ is the space of all functions in the Sobolev space $H^2(\Omega)$ with Neumann zero boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness \cite{JACOBSEN},

We choose the $i$th weighting function, $w_i$, to be the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

We compute convolution kernels $\convkernel_{x_i}$ in batches by applying $\Aop$ to a small number Dirac combs. Each application of $\Aop$ to a Dirac comb yields one batch of impulse responses, $\impulseresponse_{x_i}$, which yields one batch of convolution kernels, $\convkernel_{x_i}$. The Dirac comb, $\diraccomb_k$, associated with a batch of sample points, $\pointbatch_k$, is the sum of Dirac distributions (point sources) centered at the points $x_i \in \pointbatch_k$. That is,
\begin{equation*}
	\diraccomb_k := \sum_{x_i \in \pointbatch_k} \delta_{x_i}.
\end{equation*}
For each batch $\pointbatch_k$, we compute the action of $\Aop$ on the associated Dirac comb:
\begin{equation}
	\label{eq:dirac_comb_H_action}
	\combresponse_k := \left(\Aop \diraccomb_k^*\right)^*.
\end{equation}
By linearity, the resulting function $\combresponse_k$ may be written as
\begin{equation}
	\label{eq:phi_b}
	\combresponse_k = \left(\Aop \left(\sum_{x_i \in \pointbatch_k} \delta_{x_i}\right)^*\right)^* = \sum_{x_i \in \pointbatch_k} \left(\Aop \delta_{x_i}^*\right)^* = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i}.
\end{equation}
Since the points $x_i$ are chosen so that the ellipsoid $E_{x_i}$ that (approximately) supports $\impulseresponse_i$, and the ellipsoid $E_{x_j}$ that (approximately) supports $\impulseresponse_j$ do not overlap when $i \neq j$, from \eqref{eq:convolution_kernel} and \eqref{eq:phi_b} we have (approximately)
\begin{equation}
\label{eq:varphi_eval}
	\convkernel_{x_i}(z) = \impulseresponse_i(z+x_i) = 
	\begin{cases}
		\combresponse_k(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}
	\end{cases}
\end{equation}
for all $x_i \in \pointbatch_k$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover the convolution kernels $\convkernel_{x_i}$ associated with every point $x_i \in \pointbatch_k$.

>>>>

We choose the $i$th weighting function, $w_i$, to be the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $j \neq i$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

@@

We compute convolution kernels $\convkernel_{x_i}$ in batches by applying $\Aop$ to a small number Dirac combs. The Dirac comb, $\diraccomb_k$, associated with a batch of sample points, $\pointbatch_k$, is the sum of Dirac distributions (point sources) centered at the points $x_i \in \pointbatch_k$. That is,
\begin{equation*}
	\diraccomb_k := \sum_{x_i \in \pointbatch_k} \delta_{x_i}.
\end{equation*}
For each batch $\pointbatch_k$, we compute the action of $\Aop$ on the associated Dirac comb:
\begin{equation}
	\label{eq:dirac_comb_H_action}
	\combresponse_k := \left(\Aop \diraccomb_k^*\right)^*.
\end{equation}
By linearity, the resulting function $\combresponse_k$ may be written as follows:
\begin{equation}
	\label{eq:phi_b}
	\combresponse_k = \left(\Aop \left(\sum_{x_i \in \pointbatch_k} \delta_{x_i}\right)^*\right)^* = \sum_{x_i \in \pointbatch_k} \left(\Aop \delta_{x_i}^*\right)^* = \sum_{x_i \in \pointbatch_k} \impulseresponse_{x_i}.
\end{equation}
Since the points $x_i$ are chosen so that the ellipsoid $E_{x_i}$ that (approximately) supports $\impulseresponse_i$, and the ellipsoid $E_{x_j}$ that (approximately) supports $\impulseresponse_j$ do not overlap when $i \neq j$, from \eqref{eq:convolution_kernel} and \eqref{eq:phi_b} we have (approximately)
\begin{equation}
\label{eq:varphi_eval}
	\convkernel_{x_i}(z) = \impulseresponse_i(z+x_i) = 
	\begin{cases}
		\combresponse_k(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}
	\end{cases}
\end{equation}
for all $x_i \in \pointbatch_k$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover the convolution kernels $\convkernel_{x_i}$ associated with every point $x_i \in \pointbatch_k$.
